Dynamic Transition Analysis with TIMES

### 2018-01-12 doc/poster.tex

@@

\begin{description}
        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
                 consumption by sector (commercial, industrial, residential, 
                 building etc). 
         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
                 (i.e. energy intensity, thermal energy efficiency, 
                 transmission capacity).. 
         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
                 transition as a constrained optimization problem will
                 drive insights.
 \end{description}

>>>>

%-----------------------------------------------------------
% KNOWN ISSUE IN TIKZ MATH: tiny big symbols, like sum.
%-----------------------------------------------------------

% declare `cmex` to be arbitrary scalable
\DeclareFontShape{OMX}{cmex}{m}{n}{
  <-7.5> cmex7
  <7.5-8.5> cmex8
  <8.5-9.5> cmex9
  <9.5-> cmex10
}{}

\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}

@@

\begin{description}
        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
                 consumption by sector (commercial, industrial, residential, 
                 building etc). 
         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
                 (i.e. energy intensity, thermal energy efficiency, 
                 transmission capacity). 
         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
                 transition as a constrained optimization problem will
                 drive insights.
 \end{description}

         The key objective function is minimization of carbon emissions in 2050 
         and a key
         constraint will be that deployed generation capacity must meet energy 
         demand. This can na\"ively be written:

\begin{align}
        \intertext{minimize:}
        &\sum_g^G C_g x_g 
        \intertext{subject to:}
        &\sum_g^Gx_g = d
        \intertext{where}
        C_g =& \mbox{ carbon emissions from generation component g}\\
        x_g =& \mbox{ deployment of generation component g}\\
        d =& \mbox{ generation demand}
\end{align}

A simple \textbf{static} formulation is straightforward to write, as above.  
However this  formulation is quickly complicated by including \textbf{dynamic 
time} as well as additional constraints (energy storage, variable demand, 
$CO_2$ sequestration, efficiency, costs, etc.)
\end{block}
